\documentclass[phd,tocprelim]{cornell}
\let\ifpdf\relax
%
% tocprelim option must be included to put the roman numeral pages in the
% table of contents
%
% The cornellheadings option will make headings completely consistent with
% guidelines.
%
% This sample document was originally provided by Blake Jacquot, and
% fixed up by Andrew Myers.
%
%Some possible packages to include
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{hangcaption}
\usepackage{txfonts}
\usepackage{palatino}
\usepackage{bm}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{tikz}

\newtheorem{defn}{Definition}
\newtheorem{claim}{Claim}
\newtheorem{thm}{Theorem}[section]
\newtheorem{pros}[thm]{Proposition}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lemmas}[thm]{Lemma}
\newtheorem{cors}[thm]{Corollary}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{algs}{Algorithm}
\newtheorem{theorem}[thm]{Theorem}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{fact}[thm]{Fact}

%if you're having problems with overfull boxes, you may need to increase
%the tolerance to 9999
\tolerance=9999

\bibliographystyle{plain}
%\bibliographystyle{IEEEbib}

\renewcommand{\caption}[1]{\singlespacing\hangcaption{#1}\normalspacing}
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.75}

\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator*{\Var}{Var}

\title {Some Resource Allocation Problems}
\author {Chaoxu Tong}
\conferraldate {February}{2016}
\degreefield {Ph.D.}
\copyrightholder{Chaoxu Tong}
\copyrightyear{2016}

\begin{document}

\maketitle
\makecopyright

\begin{abstract}
We include three works on resource allocation in this thesis. Proper pricing
helps the system to allocate resource efficiently. However, the computational
efforts to obtain such prices are not always easy. In airline network revenue
setting, high-quality bid prices can be obtained via approximate dynamic
programming approach. However, this leads to an exponential-size linear program
which is slow to solve. We show that this large linear program is actually
equivalent to a compact linear program with appealing interpretation
by exploiting the minimum-cost network flow structure of this problem.
Computational experiments indicate that our results can speed up the computation
for the approximate linear programming approach by a factor ranging between 13 and 135.

In the second chapter, we study how to better serve clients by allocating resources
to open facilities with right location and type. We extend the classical \textit{facility location}
problem by associating \textit{types} with the facilities and the clients. The types define a partial
ordering and a client can only be served by facilities of equal or higher type. We show
how to obtain approximation algorithms for two interesting special cases.
We also study the problem embedded in time, which is known as the lot-sizing variant.
We give algorithm that finds optimal solution for the variant.

In the third chapter, we study how to allocate medical resource in imaging facilities.
The most common method to allocate imaging machine time is by a appointment system.
However, despite the best efforts by medical staff, the inherently stochastic nature of the duration of various procedures and
unexpected disruptions can bring considerate congestion to the system. In the multi-site setting,
we seek to complement appointment scheduling with real-time resource sharing.
By monitoring system status and making prediction of future, we can identify
potential congestions and divert patients accordingly to prevent these congestions
from happening. We provide simulation results showing that this method improves
patient waiting time and facilities overtime, which are two important quality measurements.
\end{abstract}

\begin{biosketch}
Chaoxu grew up in a small town, Tongling, Anhui in China. He enjoys cooking and movies.
\end{biosketch}

\begin{dedication}
To my parents and my wife.
\end{dedication}

\begin{acknowledgements}
A big thanks to David and Shane for being such kind and patient advisors.
Also, I would like to thank all committee members for providing
invaluable feedbacks on this thesis.
Thanks all friends I met here at Ithaca for sharing precious time with me.
Also thank the passing time for giving me refreshed understanding of myself.
\end{acknowledgements}

\contentspage
\tablelistpage
\figurelistpage

\normalspacing \setcounter{page}{1} \pagenumbering{arabic}
\pagestyle{cornell} \addtolength{\parskip}{0.5\baselineskip}

\input{chap1/approximate_lp_rm}
\input{chap2/paper}
\input{chap3/main}
%\input{logit_mixture/logit_mixture}
%\input{other/main}

\bibliography{chap1/ref,chap2/myrefs,chap3/ref}

\end{document}
